### 2020-03-09 Article.tex
Demos hechas

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[\tau_{(T_1,v_1)}(u)\morph{k} \tau_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

	\end{itemize}
\end{itemize}

@@

\subsection{Probabilistic results}

@@

\begin{theorem} \label{thm:BrunSieve}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{lemma}
	Let $H$ be an hypergraph. Then 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
\end{lemma}
\begin{proof}
Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
the indicator variable
that takes value one when $f$ defines an monomorphism 
between $H$ and $G_n$ and zero otherwise. 
The probability that $X^H_{n,f}=1$ is exactly
$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
$C$ that does not depend on $f$ nor $n$. Define 
$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
Taking into account that 
\[
\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
\]
the result follows. 
%Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
% $\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
% $\overbar{h}$ be an ordering of the vertices
%in $V(H)$. For any list 
% $\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
%let $X_{\overbar{v}}$ be the random indicator variable
%that takes value $1$ if the natural map 
% $f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
%between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
%with probability
% $ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
% $
%and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
%all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
%copies of $H$ are in $G_n$. Thus, 
%\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
%= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
%\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
%\]
%The expected number of copies of $H$ in $G_n$ is then this last
%expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
%In consequence,
%\begin{align*}
% &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
%=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
%\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
%\end{align*}
%and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
\end{proof}

As a corollary of last result we get the following:  
\begin{lemma} \label{lem:nocopiesdense}
	Let $H$ be an hypergraph such that $ex(H)>0$. Then
	a.a.s there are no copies of $H$ in $G_n$. 
\end{lemma}  
\begin{proof}
	Because of the previous fact, 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
	\xrightarrow[]{n\to \infty} 0$. An application of the first moment
	method yields the desired result. 
\end{proof}

@@

\begin{lemma}\label{lem:nocopiesfixed}
	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
	Let $H$ be an hypergraph such that $ex(H)>-j$. 
	Then a.a.s there is no copy of $H$ in $G_n$ that
	contains all $v_1,\dots,v_j$. 
\end{lemma} 
\begin{proof}
It is sufficient to show that
\begin{equation}\label{eqn:aux}
\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
\end{equation}
Then, because of a first moment argument the result follows.\par
Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
Let 
\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
\overline{x}\subset Im(f)}} X^H_{n,f}.\]
The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
is $\Theta(n^{v(H)-j})$. In consequence 
$
\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
$, and 
\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
\overline{v} \big]=\Theta(n^{-ex(H)-j}).
\]
This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
\end{proof}

@@

\begin{definition} 
	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
	$\chi: V(G) \rightarrow \Sigma$.  
	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
	an isomorphism between them is an hypergraph isomorphism 
	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
	for any $v\in V(H)$. 
	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
	isomorphism from $(G,\chi)$ to itself. As with the case of
	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
	automorphisms of $(G,\chi)$.
	\par
	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
	Then a copy of $H$ in $G$ is
	a sub-hypergraph $H^\prime\subset G$ such that 
	$(H,\rho)$ is isomorphic to 
	$(H^\prime,\chi|_{_{H^\prime}})$.\par
	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
	define the set $Copies(S,(G, \chi))$ as the one that contains all 
	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
	such that $V(H)\subset S$.
	Notation: $H\subset_{\Sigma}G$.

\end{definition}

@@

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
	(i.e., an hypergraph consisting of only one edge), $v\in V(e)$ is a vertex called the root 
	of $e$, and $\chi: V(e)\rightarrow \Sigma$ such that $\chi(u)=\emptyset$ if and only if 
	$u=v$.\par
	Given a rooted $\Sigma$-edge $(e,v,\chi)$, a set $V$ and a 
\end{definition}

\begin{definition}

\end{definition}

@@

%$[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices

>>>>

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$. Let $\Sigma_r$
	be the set consisting of the root symbol $\tau$ and
	the $k$-equivalence classes of trees with radius lesser than $r$.
	Given a rooted tree $(T,v)$ with whose radius is lesser than $r$
	we define its canonical $\Sigma_r$-coloring as the map 
	$\chi_{(T,v)}: V(T)\rightarrow \Sigma_r$ satisfying that
	$\chi_{(T,v)}(u)$ is the $k$-equivalence class of $\mathrm{Tr}(u,T;v)$
	for any $u\neq v$ and $\chi_{(T,v)}(v)=\tau$. \par
	Let $T_1$ and $T_2$ be rooted trees with radius
	at most $r+1$. We say that $(T_1,v_1)\simeq_k (T_2,v_2)$ 
	if given any $\Sigma_r$-pattern $(e,\chi)$ the 
	"quantity of initial edges $e_1\prime\in E(T_1)$ such that
	$(e,\chi)\simeq (e_1,\chi_{(T_1,v_1)})$" and the
	"quantity of initial edges $e_2\prime\in E(T_2)$ such that
	$(e,\chi)\simeq (e_2,\chi_{(T_2,v_2)})$" are the same or
	are both greater than $k-1$.
\end{itemize}

@@

\section{Probabilistic results}
\subsection{Convergence to Poisson variables}

@@

\begin{theorem} \label{thm:BrunSieve}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} \binom{X_{n,i}}{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{lemma}
	Let $H$ be an hypergraph. Then 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
\end{lemma}
\begin{proof}
It holds
\[
 \mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
 \sum_{H^\prime \in Copies(H,[n])} \PR{H^\prime \subset G_n}.
\]	
We have that $|Copies(H,[n])|=\frac{(n)_{v(H)}}{|Aut(H)|}$. Also, 
for any $H^\prime \in Copies(H,[n])$ it is satisfied
\[
\PR{H^\prime \subset G_n}= \prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}} 
\right)^{e_R(H)}.
\]
Substituting in the first equation we get
\[
\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
\frac{(n)_{v(H)}}{|Aut(H)|}\cdot
\prod_{R\in \sigma} \left(\frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
\underset{n \to \infty}{\sim}
n^{-ex(H)} \cdot \frac{\prod_{R\in \sigma} \beta_R^{
e_R{H} }}{|Aut(H)|}.
\]

%Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
%the indicator variable
%that takes value one when $f$ defines an monomorphism 
%between $H$ and $G_n$ and zero otherwise. 
%The probability that $X^H_{n,f}=1$ is exactly
%$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
%be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
%$C$ that does not depend on $f$ nor $n$. Define 
%$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
%copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
%Taking into account that 
%\[
%\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
%\]
%the result follows. 
%Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
% $\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
% $\overbar{h}$ be an ordering of the vertices
%in $V(H)$. For any list 
% $\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
%let $X_{\overbar{v}}$ be the random indicator variable
%that takes value $1$ if the natural map 
% $f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
%between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
%with probability
% $ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
% $
%and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
%all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
%copies of $H$ are in $G_n$. Thus, 
%\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
%= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
%\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
%\]
%The expected number of copies of $H$ in $G_n$ is then this last
%expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
%In consequence,
%\begin{align*}
% &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
%=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
%\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
%\end{align*}
%and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
\end{proof}

As a corollary of last result we get the following:  
\begin{lemma} \label{lem:nocopiesdense}
	Let $H$ be an hypergraph such that $ex(H)>0$. Then
	a.a.s there are no copies of $H$ in $G_n$. 
\end{lemma}  
\begin{proof}
	Because of the previous fact, 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
	\xrightarrow[]{n\to \infty} 0$ . An application of the first moment
	method yields the desired result. 
\end{proof}

@@

\subsubsection{Rooted hypergraphs}

A rooted hypergraph $(G,\overline{u})$ is an hypergraph $H$ together with 
an ordered sequence of distinguished vertices $\overline{u}\in (V(H))_*$.
An isomorphism between two rooted hypergraphs $(G,\overline{u})$ and
$(H,\overline{v})$ is a map $f: V(G)\rightarrow V(H)$ such that $f$
is an isomorphism between $G$ and $H$ that satisfies the additional condition
$f(\overline{u})=\overline{v}$. An automorphism of $(G,\overline{u})$  is 
an isomorphism from $(G,\overline{u})$  to itself. 
We write $Aut(G,\overline{u})$ to denote the group
of automorphisms of $(G,\overline{u})$. \par

Given a rooted hypergraph $(G,\overline{u})$, a set of vertices
$V$ and a list $\overline{v}\in (V)_*$ such that $len(\overline{u})
= len(\overline{v})$ we define the set $Copies((G,\overline{u}),
(V,\overline{v}))$ as the set of rooted hypergraphs 
$(H,\overline{v})$ isomorphic to $(G,\overline{u})$ such that
$V(H)\subset V$. \par

\begin{lemma}\label{lem:nocopiesfixed}
	Let $(H,\overline{u})$ be a rooted hypergraph. Let
	$\overline{v}\in (\N)_*$ be a list of vertices satisfying
	$len(\overline{u})=len(\overline{v})$. For each $n\in \N$ 
	let $X_n$ be the random variable that
	counts the copies $(H^\prime,\overline{v})\in
	Copies((H,\overline{u}),
	([n],\overline{v}))$ that are contained in $G_n$. Then
	$\mathrm{E}\big[ X_n \big]=\Theta(n^{-ex(H)-len(\overline{u})})$.	
\end{lemma}
\begin{proof}
	It holds
	\[
	\mathrm{E}\big[ X_n \big]=\sum_{H^\prime\in (H^\prime,\overline{v})\in
		Copies((H,\overline{u})} \PR{H^\prime \subset G_n}
	= \frac{(n)_{(v(H)-len(\overline{u}))}}{|Aut(H,\overline{u})|} 
	\cdot\prod_{R\in\tau} \left( \frac{\beta_R}{n^{ar(R)-1}}\right)^{e_R(H)}
	\]
\end{proof}

%
%\begin{lemma}
%	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
%	Let $H$ be an hypergraph such that $ex(H)>-j$. 
%	Then a.a.s there is no copy of $H$ in $G_n$ that
%	contains all $v_1,\dots,v_j$. 
%\end{lemma} 
%\begin{proof}
%It is sufficient to show that
%\begin{equation}\label{eqn:aux}
%\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
%\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
%\end{equation}
%Then, because of a first moment argument the result follows.\par
%Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
%As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
%variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
%and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
%$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
%Let 
%\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
%\overline{x}\subset Im(f)}} X^H_{n,f}.\]
%The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
%is $\Theta(n^{v(H)-j})$. In consequence 
%$
%\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
%$, and 
%\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
%\overline{v} \big]=\Theta(n^{-ex(H)-j}).
%\]
%This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
%\end{proof}

@@

\begin{definition} 
	Given a set $\Sigma$, a $\Sigma$-hypergraph is a pair
	$(G,\chi)$ consisting of an hypergraph $G$ and a map 
	$\chi: V(G) \rightarrow \Sigma$.  
	Given two $\Sigma$-hypergraphs $(H,\rho)$ and $(G,\chi)$,
	an isomorphism between them is an hypergraph isomorphism 
	$f:V(H)\rightarrow V(G)$ satisfying $\rho(v)=\chi(f(v))$
	for any $v\in V(H)$. 
	An automorphism of a $\Sigma$-hypergraph $(G,\chi)$ is an
	isomorphism from $(G,\chi)$ to itself. As with the case of
	hypergraphs we write $Aut(G,\chi)$ to denote the group of 
	automorphisms of $(G,\chi)$.
	\par
	Let $(H,\rho), (G,\chi)$ be two $\Sigma$-hypergraphs. 
	Then a copy of $H$ in $G$ is
	a sub-hypergraph $H^\prime\subset G$ such that 
	$(H,\rho)$ is isomorphic to 
	$(H^\prime,\chi|_{_{H^\prime}})$.\par
	Given a $\Sigma$-hypergraph $(G,\chi)$ and a set $V$ we
	define the set $Copies(S,(G, \chi))$ as the one that contains all 
	possible $\Sigma$-hypergraphs $(H,\rho)$ isomorphic to $(G,\chi)$ 
	such that $V(H)\subset S$.	
\end{definition}

@@

\begin{definition}
	Let $\Sigma$ be a set containing the empty label $\emptyset$. A rooted $\Sigma$-edge
	is a $\Sigma$-hypergraph $(e,\chi)$ where $e$ is an edge 
	(i.e., an hypergraph consisting of only one edge), and there is a unique vertex
	$v\in V(e)$ such that $\chi(v)=\emptyset$.
	Given a rooted $\Sigma$-edge $(e,\chi)$, a set of vertices $V$ and a vertex $v\in \N$
	we define the set $Copies((e,\chi),(V,v))$ as the set of copies 
	$(e^\prime, \chi^\prime) \in  Copies((e,\chi),V)$ such that $v$ is
	the root of $(e^\prime,\chi^\prime)$.
\end{definition}

\begin{definition} 
	Let $V\subset \N$ be a finite set of vertices. 
	Let $\Sigma_1,\dots, \Sigma_k$ be sets containing the empty label 
	$\emptyset$. For each $i\in [k]$ and each $n\in \N$
	let $\chi_i^n$ be a random $\Sigma_i$-coloring
	of $G_n$ satisfying that the succession $(\chi_i^n)_{n\in \N}$ is
	$V$-regular. We say that the sequences $(\chi_1^n)_{n\in \N},
	\dots, (\chi_k^n)_{n\in \N}$ are asymptotically independent
	with respect to edges intersecting $V$ if for any given
	\begin{itemize}
		\item fixed finite set of edges $S\subset E(\N)$ such that any edge $e\in S$ 
		contains some vertex in $V$,
		\item fixed disjoint sets of vertices $V_1,\dots, V_k \subset \bigcup_{e\in S}e$ 
		satisfying $V\cup V_i=\emptyset$ for all $i\in [k]$, and
		\item for each $i\in [k]$ and $v\in V_i$ a fixed label $s(v)\in \Sigma_i$
		different from the empty label,
	\end{itemize}
	it is satisfied 
	\[
	\Ln \mathrm{Pr}\big(
	\bigwedge_{i=1}^k \bigwedge_{v\in V_i} \chi_{n,i}(v)=s(v)
	\, \big| \, \bigwedge_{e\in S} e\subset G_n \,
	\big) = \prod_{i=1}^k \prod_{v\in V_i} \mathrm{Pr}\big[\chi_i=s(v)
	\big]		
	\]
\end{definition}

\begin{theorem}
	\begin{theorem}
		Let $k\in \N$.	For each $i\in [k]$ 
		\begin{itemize}
			\item Let $v_i\in \N$ be a vertex. Define $V:=\{v_1,\dots,v_k\}$.
			\item Let $\Sigma_i$ be a set containing the empty label, and let $S_i$ be a set
			of non-isomorphic rooted $\Sigma_i$-edges. 
			\item For each $n\in \N$ let $\chi^i_n$ be random $\Sigma_i$-coloring
			$G_n$ satisfying that the succession $(\chi^i_n)_{n\in \N}$ is $V$-regular. 
			\item For each $(e,\rho)\in S_i$, let $X^{(e,\rho)}_{n,i}$ be the random 
			variable that counts the number of copies in $Copies((e,\rho),([n],v_i))$
			that appear in $(G_n,\chi^i_n)$.				
		\end{itemize}
		Suppose that the
		successions $(\chi^1_n)_{n\in\N}, \dots, (\chi^k_n)_{n\in\N}$
		are independent with respect to edges intersecting $V$.
		Then, for any fixed natural numbers 
		$(a^{(e,\rho)}_{i})_{i\in [k], (e,\rho)\in S_i}$ it holds
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k \bigwedge_{(e,\rho)\in S_i}
		 X_{n,i}=a^{(e,\rho)}_i  \big)=
		\prod_{i=1}^{k}e^{-\lambda_i}\frac{\lambda_{(e,\rho)}^{a^{(e,\rho)}_i}}{{a^{(e,\rho)}_i}!},
		\]
		where for each $i\in [k]$,
		\[
		\lambda_{(e,\rho)}:= \frac{1}{|Aut(e,\rho)|} 
		\prod_{v\in V(e), \rho(v)\neq \emptyset}
		\mathrm{Pr}\big[\chi^i=\rho^i(v)\big].
		\]
	\end{theorem}
\end{theorem}

@@

% $[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
